Checkpoint 4

### 2020-05-01 Draft-Report.Rmd
F

@@

*White, StateColor, Day, Positive Cases, State

@@

complexmod <- stan_glmer(
  ChinaVirusInterest ~ Day + StateColor + percent_white + positive + (Day | State), 
  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
)
```

@@

```{r}
pp_check(complexmod, nreps = 50)
```

@@

new_data <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive_rate = 0.11) 
new_pred <- posterior_predict(
  complexmodel,
  newdata = new_data)

>>>>

################ FEDDY PREDICT FOR FLORIDA TOO please. ALSO MOVE YOUR STUFF TO THE RIGHT PLACES ############

@@

*White, StateColor, Day, Total test Results, State

@@

complexmod <- stan_glmer(
  ChinaVirusInterest ~ Day + StateColor + percent_white + totalTestResults + (Day | State), 
  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
)
```

@@

```{r}
pp_check(complexmod, nreps = 50)
```
The assumption of using a Normal model is fairly reasonable besides the fact that we observe two bumps on both sides of the tails. We can assume these to be outliars.

@@

new_data <- Finaldata %>% filter(State == "FL")
new_pred <- posterior_predict(
  complexmodel,
  newdata = new_data)
